\documentclass{myarticle}

\title{\textbf{\href{http://dx.doi.org/10.1139/cgj-2016-0037}{Correlations for undrained shear strength of Finnish soft clays.}\\芬兰软黏土不排水剪切强度的相关性}}
\date{\today}
\author{Marco D’Ignazio\thanks{
    \textbf{M. D’Ignazio* and T.T. Länsivaara.}Department of Civil Engineering, Tampere University of Technology, Korkeakoulunkatu 5, 33720, Tampere, Finland.
} \and Kok-Kwang Phoon\thanks{
    \textbf{K.-K. Phoon and S.A. Tan.}Department of Civil and Environmental Engineering, National University of Singapore, No. 1 Engineering Drive 2, 117576, Singapore.
} \and Siew Ann Tan \and Tim Tapani Länsivaara\thanks{
    \textbf{Corresponding author:} Marco D’Ignazio (emails: \url{marco.dignazio@tut.ﬁ}; \url{marco.dignazio@ngi.no}).\newline{}
    \indent{}~*Present address: Norwegian Geotechnical Institute (NGI), Sognsveien 72, N-0855 Oslo, Norway.\newline{}
    \indent{}~Copyright remains with the author(s) or their institution(s). Permission for reuse (free in most cases) can be obtained from \href{https://www.nrcresearchpress.com/page/authors/services/reprints}{RightsLink}.\newline{}\newline{}
    \indent{}~Can. Geotech. J. 53: 1628–1645 (2016) \href{http://dx.doi.org/10.1139/cgj-2016-0037}{dx.doi.org/10.1139/cgj-2016-0037}
}}

\begin{document}

\maketitle

\section*{Abstract 摘要}

\begin{Parallel}{0.60\textwidth}{}
    \ParallelLText
    {
        The study focuses on the derivation of transformation models for undrained shear strength ($s_u$) of Finnish soft sensitive clays. Speciﬁc correlation equations for $s_u$ of Finnish clays are presented in this work for the ﬁrst time. Field and laboratory measurements from 24 test sites in Finland are exploited for this purpose and a multivariate database is constructed. The multivariate data consist of $s_u$ from the ﬁeld vane test, preconsolidation stress, vertical effective stress, liquid limit, plastic limit, natural water content, and sensitivity. The main objective is to evaluate the interdependence of $s_u$, consolidation stresses, and index parameters and provide a consistent framework for practical use. The new correlations are established through regression analyses. The constructed framework is further validated by another independent multivariate database of clays from Sweden and Norway as well as by empirical equations for Swedish and Norwegian clays. Existing correlations are evaluated for Finnish and Scandinavian clays. Finally, bias and uncertainties of the new correlations are presented.

        \textbf{Key words: }global transformation models, soft clays, multivariate database, undrained shear strength.
    }
    \ParallelRText
    {
        这项研究着重于芬兰软黏土不排水抗剪强度（$s_u$）转换模型的推导。芬兰黏土的特殊的相关方程是第一次在这项工作中提出。为此，利用了芬兰24个测试点的现场和实验室测量值，并建立了一个多元数据库。多元数据由现场叶片试验，预固结应力，垂直有效应力，液体极限，塑性极限，天然水含量和敏感性组成。主要目的是评估$s_u$，固结应力和指标参数的相互依赖性，并为实际使用提供一致的框架。通过回归分析建立新的相关性。另一个来自瑞典和挪威的黏土的独立多元数据库以及瑞典和挪威黏土的经验公式进一步验证了构建的框架。对芬兰和斯堪的纳维亚黏土的现有相关性进行评估。最后，提出了新的相关性的偏差和不确定性。

        \textbf{关键词：}全局转换模型，软黏土，多元数据库，不排水剪切强度。
    }
\end{Parallel}

\input{sections/section-1.tex}
\input{sections/section-2.tex}

\begin{appendix}
\end{appendix}

\bibliographystyle{plainnat} % gbt7714-author-year gbt7714-numerical
\bibliography{DIgnazio2016.bib}

\end{document}